Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-04-02 thesis/chapters/ch_chapter4.tex
Updates to results in CH4 and figures... nearing end of draft of this

For clarity we focused on the \textit{mean} evolution of individual enrichment events at fixed injection energy in the results thus far, but we turn now to discuss how much variety exists among these individual events. For each of the discussed runs (from set II), Figure~\ref{ch4:fig:CGM_CNM_variance} shows the fraction of metals ejected from the galaxy (left) and the fraction of metals in the ISM within the CNM (right) as a function of source energy at two different times, 20~Myr (blue) and 100~Myr (orange). The averaged values at each energy are shown as points, and the bars denote the min/max value for each event energy.\footnote{While the standard deviation or IQR may be more informative here, rather than min / max, the sample size at each energy, with the exception of the E46 runs, is too small to reliably do so.} As shown, there is substantial variation at each energy. This is particularly striking for the E46 events, which seemingly can have effectively any value for $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ at any point during the evolution. It is clear that the trends discussed thus far applies to the average behavior of events at a fixed $E_{\rm ej}$, but not for an individual event. In addition, a higher $E_{\rm ej}$ seems to increase the minimum $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ expected, but the behavior of any one event must depend on additional factors.

 \begin{figure*}
   \centering
   \includegraphics[width=0.8\linewidth]{figures/ch4/II_Eej_CNM_avg}
   \caption{A summary of the results presented in Figure~\ref{ch4:fig:CGM_CNM} that demonstrate the significant variation in $f_{\rm CGM}$ and
   $f_{\rm CNM} / f_{\rm Disk}$ at fixed injection energy. The points give the average values at each energy at two different times, while the
   error bars show the min/max values at each energy. The points at different times have been offset slightly along the horizontal axes for clarity. Since they are only two points, we show the results from II\_E52\_r0 and II\_E52\_r300 without averaging.}
   \label{ch4:fig:CGM_CNM_variance}
 \end{figure*}

But what causes this variation among individual events? Do additional properties about the injection site (ISM density, position, local SFR), determine the subsequent evolution? Or is this the result of a complex, non-deterministic set of complex interactions the metals from a given event experience over their lifetime in the galaxy? We investigate the dependence on a few of these properties below.

@@

Across runs, there is no clear dependence on the radial position of the event and the fraction of metals ejected beyond the galaxy for any of the displayed runs at either 20~Myr or 100~Myr. There is a slight increase in the minimum fraction of metals ejected from the galaxy as a function of radius for the higher energy runs ($>10^{50}$~erg). This perhaps not surprising for the largest radii as 600~pc is right near the very edge of the galaxy's disk. But again, the trend is weak and there is clearly still a great variance at both fixed $E_{\rm ej}$ and $r$.

@@

We compute the average ISM properties within a 4-zone radius ($4 \times dx$=7.2~pc) around each injection site to examine any potential correlations in evolution with ISM properties.\footnote{Note that the injection region for each event is a 3-cell radius sphere mapped onto the grid with a CIC interpolation scheme.} In Figure~\ref{ch4:fig:ISM_variance} we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ for each II run as a function of the average number density ($<n>$) in the injection region within 0.1~Myr (our time resolution) of the event.

 \begin{figure*}
   \centering
   \includegraphics[width=0.95\linewidth]{figures/ch4/II_n_dependence}
   \caption{.}
   \label{ch4:fig:ISM_variance}
 \end{figure*}

>>>>

For clarity we focused on the \textit{mean} evolution of individual enrichment events at fixed injection energy in the results thus far, but we turn now to discuss how much variety exists among these individual events. For each of the discussed runs (from set II), Figure~\ref{ch4:fig:CGM_CNM_variance} shows the fraction of metals ejected from the galaxy (left) and the fraction of metals in the ISM within the CNM (center) as a function of source energy at two different times, 20~Myr (blue) and 100~Myr (orange). In the right panel, we show how the spread at each of these times varies for each event. The averaged values at each energy are shown as points, and the bars denote the min/max value for each event energy.\footnote{While the standard deviation or IQR may be more informative here, rather than min / max, the sample size at each energy, with the exception of the E46 runs, is too small to reliably do so.} As shown, there is substantial variation at each energy. This is particularly striking for the E46 events, which seemingly can have effectively any value for $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ at any point during the evolution. Finally, the right panel shows that the degree of inhomogeneous mixing for each event varies significantly as well. However, there is a more clear trend for each of the mean, min, and max values of the spread at 100~Myr (decreasing as a function of increasing $E_{\rm ej}$).

 \begin{figure*}
   \centering
   \includegraphics[width=0.8\linewidth]{figures/ch4/II_Eej_CNM_avg}
   \caption{A summary of the results presented in Figure~\ref{ch4:fig:CGM_CNM} and Figure~\ref{ch4:fig:CGM_CNM} that demonstrates the significant variation in $f_{\rm CGM}$, $f_{\rm CNM} / f_{\rm Disk}$, and the mean-median separate at fixed injection energy. The points give the average values at each energy at two different times, while the error bars show the min/max values at each energy. The points at different times have been offset slightly along the horizontal axes for clarity. Since they are only two points, we show the results from II\_E52\_r0 and II\_E52\_r300 without averaging.}
   \label{ch4:fig:CGM_CNM_variance}
 \end{figure*}

It is clear that the trends discussed thus far applies to the average behavior of events at a fixed $E_{\rm ej}$, but not for an individual event. In addition, a higher $E_{\rm ej}$ seems to increase the minimum $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ expected, but the behavior of any one event must depend on additional factors. But what causes this variation among individual events? Do additional properties about the injection site (ISM density, position, local SFR), determine the subsequent evolution? Or is this the result of a complex, non-deterministic set of complex interactions the metals from a given event experience over their lifetime in the galaxy? We investigate the dependence on a few of these properties below.

@@

Across runs, there is no clear dependence on the radial position of the event and the fraction of metals ejected beyond the galaxy for any of the displayed runs at either 20~Myr or 100~Myr. There is a slight increase in the minimum fraction of metals ejected from the galaxy as a function of radius for the higher energy runs ($>10^{50}$~erg). This perhaps not surprising for the largest radii as 600~pc is right near the very edge of the galaxy's disk. But again, the trend is weak and there is clearly still a great variance at both fixed $E_{\rm ej}$ and $r$. The fraction of metals in the ISM that are contained within the CNM (middle row) does not show any obvious trend at E46, but does seem to generally be lowest for the higher energy sources at the outskirts of the galaxy. Finally, the radial position does seem to somewhat affect the mixing behavior. Sources at the outskirts of the galaxy tend to be more inhomogeneous than sources at smaller radii, especially at 20~Myr for the higher energy events, and the variation in behavior for these sources decreases substantially, particularly at 100~Myr. It is unclear what exactly drives these mixing differences. If feedback-driven turbulence is the dominate driver of ISM mixing in this dwarf galaxy -- as it likely is -- then sources near the center are more likely to be affected by more feedback events (due to a slightly higher $\Sigma_{\rm SFR}$) and mix more efficiently.

@@

We compute the average ISM properties within a 4-zone radius ($4 \times dx$=7.2~pc) around each injection site to examine any potential correlations in evolution with ISM properties.\footnote{Note that the injection region for each event is a 3-cell radius sphere mapped onto the grid with a CIC interpolation scheme.} In Figure~\ref{ch4:fig:ISM_variance} we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ for each II run as a function of the average number density ($<n>$) in the injection region within 0.1~Myr (our time resolution) of the event. The E46 events clearly do a better job sampling the ISM density PDF, with a slight trend of decreasing $f_{\rm CGM}$ (more retained metals) with local ISM number density. This difference is even true after 100~Myr of evoltuion, but still with significant variation at fixed $n$. The number statistics limit a conclusive result for the higher energy events, but generally there does not appear to be an obvious trend in behavior of $f_{\rm CGM}$ as a function of $n$. This is perhaps because these energies are sufficient to heat up and dramatically reduce the density of the ISM in the injection region anyway, such that $n$ before the event is not as important as it is for the E46 events which are much less dynamically important. $f_{\rm CNM} / f_{\rm Disk}$ does not display any significant variation with $n$ at 100~Myr, but is slightly elevated at 20~Myr at higher densities. There is still a variety of behavior at fixed $n$. Finally, we note no obvious trends of the spread of the metal PDFs as a function of $n$ for all but the E46 run. Again, the local ISM densities is likely not too dynamically relevant to the higher energy events -- hence their lack of variation with $n$ -- but this is not true for E46. There is a fairly clear trend of increasing inhomogeneity in the CNM as a function of the initial $n$ in the injection region for E46, that is not present at 20~Myr, but is obvious at 100~Myr.

 \begin{figure*}
   \centering
   \includegraphics[width=0.95\linewidth]{figures/ch4/II_n_dependence}
   \caption{The variation of $f_{\rm CGM}$, $f_{\rm CNM} / f_{\rm Disk}$, and the spread of the metal fraction PDFs in the ISM as a function of the local ISM number density ($n$) within the injection region of the event just prior (within 0.1~Myr) of the event. Points, lines, and line colors mean the same as shown in Figure~\ref{ch4:fig:CGM_CNM_variance}}
   \label{ch4:fig:ISM_variance}
 \end{figure*}
